### 2017-12-07 Docs/Thesis/docs/chapter4.tex
update

In this chapter we are going to go in deep details on some implementations and modelling approaches mentioned in the last chapter.

In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise. The problem we want to adress are these one:

@@

	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way.

@@

Many works have been made in second point on the literature, but not so many on the second. So we are proposing a model, and validating it.

In the second section, we will describe breifely two others we used to calc flow's session ON and OFF times, and

@@

%2nd-review
In this chapter, we propose a method automatizable by  software. We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}. Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.

%2nd-review
We made a brief bibliographic review of some related works on this topic. Then, we will present the traffic traces we are going to use in this chapter, and in the rest of our work. After we present or selected method for parameterization and fitting choice. To test our criteria quality, we define a validation method, based on cross-validations made by simulations.

\subsection{Related Works}

%2nd-review
There are plenty of works on the literature which proposes new processes and methodologies for modeling times between packets and packet trains.

%2nd-review
Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources. The model emulates a multiple source power-tail Markov-Modulated (PT-MMPP) ON/OFF process, where the ON times are power-tail distributed. They achieve analytical performance measurements using Linear Algebra Queueing Theory.

%2nd-review
Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a super computer. They show that the Weibull probability functions are able to express well small and high values of inter-job submission times. They also tested exponential, lognormal and Pareto distributions. Exponential distribution couldn't  represent long-range values because it fell off too fast and Pareto was too slow. Lognormal fit well small values, but was poor on larger ones.

%2nd-review
Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a model of scheduling traffic of many heavy-tail sources. On his work, he uses many Pareto sources to represent the traffic. To estimate the shape parameter $\alpha$ they use linear regression.

@@

\subsection{Methodology}

@@

\subsubsection{Validation}

@@

\subsection{Results}

@@

Also the order of the stochastic function tend to not differ much. We are able to conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choise.

Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes. The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one. The models selected as the worsts usually returned poor results.

Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments. For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.

@@

@@

\section{Others Algorithms and Methods}

In this section we breef present another methods used by the \textit{TraceAnalyzer} component. The first to calculate the session ON and OFF times. The second classify applications based on its tranport protocol and ports. In the table ~\ref{tab:mehtods} we summarize the stack of models used to create the Compact Trace Descriptor (CTD file).

\subsection{On/Off Times estimation}

@@

\subsection{Application classification}

@@

%\begin{table}[ht!]
%	\centering
%	\caption{Stack of models used to create the CTD file}
%	\label{tab:mehtods}
%	\begin{tabular}{|l|l|}
%		\hline
%		Layer & Method \\
%		\hline
%		Link Layer  & \multirow{3}{*}{Packets header's data} \\ \cline{1-1}\cline{3-3}
%		
%		Network Layer & \\ \cline{1-1}\cline{3-3}
%		
%		Transport Layer & \\ \hline
%		
%		Application Layer  & Application Match Table  \\ \hline
%		
%		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$  \\ 
%
%		%\cline{2-2}\cline{3-3}  
%		& Algorithm: $stochasticModelFitting$ \\  \hline
%
%		Packet Sizes  & Algorithm: $stochasticModelFitting$ \\ \hline
%
%	\end{tabular}
%\end{table}

>>>>

In this chapter we are going to go in deep details on some implementations and modelling approaches mentioned in the last chapter. In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise. The problem we want to adress are these one:

@@

	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way, avoiding human analyzis;

@@

In the second section, we will describe and discuss the methods we used to estimate the packet-trains sizes (ON/OFF times), and to do the application classification. The calculation of the packet trains periods in our model is deterministic. The \textit{compact trace descriptor} stores the same ON and OFF times from each flow from the original traffic trace. The application classification is made by a match table of transport protocols and ports.

@@

There are plenty of works on the literature which proposes new processes and methodologies for modeling times between packets and packet trains. Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources. The model emulates a multiple source power-tail Markov-Modulated (PT-MMPP) ON/OFF process, where the ON times are power-tail distributed. They achieve analytical performance measurements using Linear Algebra Queueing Theory. Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a super computer. They show that the Weibull probability functions are able to express well small and high values of inter-job submission times. They also tested exponential, lognormal and Pareto distributions. Exponential distribution couldn't  represent long-range values because it fell off too fast and Pareto was too slow. Lognormal fit well small values, but was poor on larger ones. Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a model of scheduling traffic of many heavy-tail sources. On his work, he uses many Pareto sources to represent the traffic. To estimate the shape parameter $\alpha$ they use linear regression.

%2nd-review
In this chapter, we propose a method automatizable by  software. We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}. Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical. We show the traffic traces we are going to use in this chapter, and in the rest of our work. After we present or selected method for parameterization and fitting choice. To test our criteria quality, we define a validation method, based on cross-validations made by simulations.

@@

\subsection{Modelling Methodology}

@@

\subsection{Modelling Method Validation}

@@

\subsection{Modelling Results}

@@

We are able to conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choise.

Except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes. The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one. The models selected as the worsts usually returned poor results.

It is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments. For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.

@@

\section{ON/OFF Periods and Application classification}

@@

In this section we breef show another methods used by the \textit{TraceAnalyzer} component. The first to calculate the session ON and OFF times. The second classify applications based on its tranport protocol and ports. In the table ~\ref{tab:methods} we summarize the stack of models used to create the Compact Trace Descriptor (CTD file).

@@

@@

\section{Conclusion}

In this section, we went on details on some methodologies mentioned in the chapter ~\ref{ch:architecture}. Here we avoid implementation and architecture concepts, and just discussed the methods. In this first section, we focused our research on develope a consistent method for automatic selection of stochastic functions for inter-packet times. Since we could not find any other methodology in the literature, we developt our own and tested if it is worth or not. The results showed our method satisfactory and had presented a reasonable prediction rate on the best functions. We now can ensure that it is a safe method and that AIC and BIC are good criterions for this sort of data.  We abstracted this method in the algorithm ~\ref{alg:stochasticModelFitting}. In the second section, we also present the methods used to estimate packet trains periods (algorithm ~\ref{alg:calcOnOff}) and make the application classification (table ~\ref{tab:application-protocols}). In the table ~\ref{tab:methods}, the usage of each method is summarized.

\begin{table}[ht!]
	\centering
	\caption{Methods used by each layer.}
	\label{tab:methods}
	\begin{tabular}{cc}
		\hline
		Layer                               & Method                                 \\ \hline
		Link Layer                          & \multirow{3}{*}{Packets header's data} \\
		Network Layer                       &                                        \\
		Transport Layer                     &                                        \\
		Application Layer                   & Application Match Table                \\
		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$                 \\
		& Algorithm: $stochasticModelFitting$    \\
		Packet Sizes                        & Algorithm: $stochasticModelFitting$    \\ \hline
	\end{tabular}
\end{table}
